Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-05-26 manuscripts/manuscript.Rmd
update references and figures

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: James Sanchirico
    affiliation: UCD
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville
abstract: |
          Ecological systems are dynamic and policies to manage them need to
          respond to that variation. However, policy adjustments will sometimes
          be costly, which means that fine-tuning a policy to track variability in
          the environment very tightly will only sometimes be worthwhile. We use a
          classic fisheries management question – how to manage a stochastically
          varying population using annually varying quotas in order to maximize
          profit  - to examine how costs of policy adjustment change optimal
          management recommendations. Costs of policy adjustment (here changes in
          fishing quotas through time) could take different forms. For example,
          these costs may respond to the size of the change being implemented or
          there could be a fixed cost any time a quota change is made. We show
          how different forms of policy costs have contrasting implications for
          optimal policies. While some types of cost act to smooth out variation in
          quotas and stock sizes, as one might have expected, others can actually
          increase variation in stock sizes and quotas through time. We also show
          that the potential economic impact on the fishery of managers assuming
          policy adjustment costs are present when in fact they are absent is much
          smaller than the impact of managers assuming such costs are absent if
          they are present.
layout: preprint      # review, 11pt
---

@@

```{r libraries, output="hide", include=FALSE, cache=FALSE}
rm(list=ls())
library("pdgControl")
library("reshape2")
library("ggplot2")
library("data.table")
library("pander")
theme_set(theme_bw())
```

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- max(fees$L1) # all have same max, at c2=0 
fees <- data.frame(c2=c2,fees)
fees <- melt(fees, id="c2")

fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))
ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

```{r apples_plot, dependson="quadcosts"}
ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

@@

```{r p1, dependson="tidy", fig.width=12}
p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
```

```{r Figure3, dependson="tidy", fig.width=12}
p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
````

@@

```{r Figure4}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + 
  xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4))

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4)) 
Fig4a
Fig4b
````

```{r Figure4S}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)

FigS4a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4))

FigS4b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4)) 
FigS4a
FigS4b
```

@@

Ecosystems are dynamic and exhibit rich patterns of variability in
both time and space. In designing management policies for ecosystems,
managers need to decide how much of that variation to respond to. Managers
could try to track variations in ecosystem dynamics very closely by
setting policies that are extremely responsive to the environment. Many
theoretical studies that seek to identify optimal policies for exploited
populations and communities adopt this approach and largely ignore the
challenges that would be involved in implementing such recommendations
[e.g., @Reed1979; @Neubert2003; @Sethi2005; @Halpern2011]. However, 
the policy process can often be much more sluggish
to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2012]. 
Moreover, stakeholders impacted by ecosystem management
may prefer some stability and not want to deal with continually changing
management recommendations [@Biais1995; @Armsworth2003;
@Patterson2007; @PattersonResimont2007; @Sanchirico2008].
In other words, whatever gains are available from fine-tuning a
policy prescription to reflect environmental variation more closely
should be traded off against potential costs associated with the more
interventionist approach to management this would require.

To illustrate these concepts, Figure 1 show an example from fisheries
management. On the left axis, the figure shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT20XX].  On the right axis the figure
also shows the catch quota for the stock that was set by the relevant
management agency [@ICCAT20XX]. Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, which could contribute to
the observed quota stability. More generally, reviews by @Biais1995 and
@Patterson2007 document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

We use a classic fisheries management question to examine how accounting
for costs of policy adjustment can change optimal policies (see also
@Ludwig1980, @Feichtinger1994, @Wirl1999). We focus on how
harvest quotas for a stochastically varying fish population can be
chosen to maximize the net present value of a fishery. Our formulation
and solution method largely follow Reed’s classic treatment on this
question, a treatment repeated widely in bioeconomic textbooks. With
his formulation, Reed showed that a constant escapement policy could be
optimal under certain conditions. Such a policy involves choosing annual
quotas that are perfectly responsive to recruitment variation in a fish
stock. In poor recruitment years, the quota is set to zero and no fishing
is allowed. But any time there is a good recruitment pulse, a quota is
set that allows the fishery to exactly compensate through harvesting,
thereby maintaining the optimal escapement level. However, in that
analysis, Reed did not account for any costs of policy adjustment, which
for such a responsive management strategy potentially could be large.

@@

Empirics suggest not always as responsive as Reed solution. Explore
conditions under which that makes sense. Idea is that regulator’s
objective sometimes may not be ‘raw’ NPV, but rather NPV with some
penalties on fast changes. Possible reasons: pure administrative
transaction cost of changing policies (reaching agreement), fishermens’
preferences for less variable quotas, processing plants’ preferences for
less variable quotas especially if tied into contracts for canning and
so forth. But we do not know what functional form of any such policy
adjustment costs takes and it will be a lot of work to estimate it. Here
we explore several plausible candidate functional forms that each
reflect different ways these policy adjustment costs could work. Would
be good to know if differences between functional forms is particularly
important.

@@

We assume that managers choose annual quotas to maximize the expected
net present value (NPV) of the fishery. We take as a base case the
situation where there are no costs associated with policy adjustment and
the managers’ objective is

@@

Taken together this objective function ([eq:objective]) and the state
equation ([eq:state_equation]) define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman’s equation.
We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.

@@

<!-- ![**Expected net present value by functional form of penalty.** Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.  The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs. ](figure/Figure_1.pdf)

-->

<!-- NOTE
Figure needs tidying up to be submission ready. Resize it – can be smaller, no color needed, bigger TickLabels, no background shading or grid. It also need the relevant horizontal and vertical lines marking to show the calibration. Choose a % reduction that corresponds to that you are choosing for what is currently labeled Figs 2&3 (sample paths) and Fig 8 – histograms. We should then adjust the text to talk to what is shown in the figure consistently – e.g. is is 25% loss or 75% of the value, etc. -->

@@

<!-- If, as discussed over email, we are going to go with just one in the main text blown up a bit bigger to make it more visible, I need to have that figure to be able to write this text around it. Note I would still present the full set in the SI. Rather than trying to recover old random seeds if not stored. Just run one anew. -->
<!-- 
For the figure in the main text, I would make a single figure with six plates – the three different adjustment costs are the columns. One row is the effect on optimal harvests and one the effect on optimal stock sizes. -->

@@

<!-- At what time relative to the dynamics in equation 1, and I would be setting up a comment why they don’t see something similar to the constant escapement policy – this is just a census time issue, but I would say it explicitly given the attention we shine on the REED result upfront.
-->

@@

When considering the first formulation of policy adjustment costs
($\Pi_1$), the first panel of Figure 2 shows a typical pattern, in which
the optimal policy tends to avoid small policy adjustments, resulting in
long periods of constant policy followed by sudden bursts of adjustment.
This results in a relatively step-like policy pattern. In contrast, the
second formulation $\Pi_2$ disproportionately penalizes large policy
adjustments. The corresponding optimal policy tracks all of the changes
made by the cost-free policy, but with smaller magnitude. This results
in a smoother $h_t$ curve, one that undershoots the larger oscillations
seen in the cost-free optimum in favor of a policy that changes
incrementally each year. Finally, the optimal policy for the third,
‘fixed fee’ formulation ($\Pi_3$) only makes large adjustments, as one
might expect, because the magnitude of the adjustment made is not
reflected in the resulting penalty. Whereas the optimal solution for
$\Pi_1$ attempts to accommodate the large oscillations at the end of the
period shown (time steps $t=47-49$) with a constant quota in between the
extremes, the fixed fee version takes the opposite approach of one very
large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES

<!--
![Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.](figure/Figure_2)

![Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs](figure/Figure_3)
-->

@@

<!--
Assuming we aren’t showing cross-correlations, I think we can probably fit these into a single four subplot figure. Cross-correlations would be a little harder but just using 5 subplots from what could have been a 6 subplot figure would also work, because a journal could just put the caption into the empty space.

@@

<!--
![Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_4a.pdf)

![Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs](figure/Figure_4b.pdf)

![Figure 5a: Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5a.pdf)

![Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.](figure/Figure_5b.pdf)
-->

@@

-   Comparison between the different functional forms – smoothing (L2)
    non-smoothing (L1), and de-stablizing (fixed).

>>>>

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviera
    affiliation: UTK
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul Armsworth 
    affiliation: UTK
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: University of Melbourne, Australia 
  - code: UTK
    address: University of Tennessee, Knoxville
abstract: |
          Ecological systems are dynamic and policies to manage them need to
          respond to that variation. However, policy adjustments will sometimes
          be costly, which means that fine-tuning a policy to track variability in
          the environment very tightly will only sometimes be worthwhile. We use a
          classic fisheries management question -- how to manage a stochastically
          varying population using annually varying quotas in order to maximize
          profit  - to examine how costs of policy adjustment change optimal
          management recommendations. Costs of policy adjustment (here changes in
          fishing quotas through time) could take different forms. For example,
          these costs may respond to the size of the change being implemented or
          there could be a fixed cost any time a quota change is made. We show
          how different forms of policy costs have contrasting implications for
          optimal policies. While some types of cost act to smooth out variation in
          quotas and stock sizes, as one might have expected, others can actually
          increase variation in stock sizes and quotas through time. We also show
          that the potential economic impact on the fishery of managers assuming
          policy adjustment costs are present when in fact they are absent is much
          smaller than the impact of managers assuming such costs are absent if
          they are present.
layout: preprint      # review, 11pt
---

@@

```{r libraries, output="hide", include=FALSE, cache=FALSE}
rm(list=ls())
library("pdgControl")
library("reshape2")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
theme_set(theme_bw())
```

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- max(fees$L1) # all have same max, at c2=0 
fees <- data.frame(c2=c2,fees)
fees <- melt(fees, id="c2")
fees <- subset(fees, variable %in% c("L1", "L2", "fixed"))

#ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

```{r apples_plot, dependson="quadcosts"}
#ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

@@

@@

```{r fishstock_trends}
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)
```

@@

Ecosystems are dynamic and exhibit rich patterns of variability in
both time and space. In designing management policies for ecosystems,
managers need to decide how much of that variation to respond to. Managers
could try to track variations in ecosystem dynamics very closely by
setting policies that are extremely responsive to the environment. Many
theoretical studies that seek to identify optimal policies for exploited
populations and communities adopt this approach and largely ignore the
challenges that would be involved in implementing such recommendations
[e.g., @Reed1979; @Neubert2003; @Sethi2005; @Halpern2011]. However, 
the policy process can often be much more sluggish
to respond to variations in ecosystem dynamics [@Walters1978; @Armsworth2012]. 
Moreover, stakeholders impacted by ecosystem management
may prefer some stability and not want to deal with continually changing
management recommendations [@Biais1995; @Armsworth2003;
@Patterson2007a; @Patterson2007b; @Sanchirico2008].
In other words, whatever gains are available from fine-tuning a
policy prescription to reflect environmental variation more closely
should be traded off against potential costs associated with the more
interventionist approach to management this would require.

To illustrate these concepts, Figure 1 show an example from fisheries
management. On the left axis, the figure shows a time series for the
estimated population size, represented as spawning stock biomass, of
west Atlantic bluefin tuna (_Thunnus thynnus_, henceforth bluefin) from
a recent stock assessment [@ICCAT20XX].  On the right axis the figure
also shows the catch quota for the stock that was set by the relevant
management agency [@ICCAT20XX]. Despite the estimated population size
declining by XX% between YYYY and ZZZZ, the quota was not changed during
this period. Instead, the quota only changed occasionally and in between
times was left unaltered. Fishery management decisions regarding this
species can be highly contentious (@Safina1998, @Sissenwine1998,
@Porch2005). Moreover, the stock is fished by fleets from many nations
with quotas being set by a multilaterial management agency through a
process of negotiation. As such, we might reasonably anticipate that
for this species there could be substantial transaction costs involved
in reaching agreement over any quota change, which could contribute to
the observed quota stability. More generally, reviews by @Biais1995 and
@Patterson2007a document many cases where changes in catch
quotas that a management agency set were more modest than changes that
would be recommended just by considering variations in stock abundance.

We use a classic fisheries management question to examine how accounting
for costs of policy adjustment can change optimal policies (see also
@Ludwig1980, @Feichtinger1994, @Wirl1999). We focus on how
harvest quotas for a stochastically varying fish population can be
chosen to maximize the net present value of a fishery. Our formulation
and solution method largely follow Reed's classic treatment on this
question, a treatment repeated widely in bioeconomic textbooks. With
his formulation, Reed showed that a constant escapement policy could be
optimal under certain conditions. Such a policy involves choosing annual
quotas that are perfectly responsive to recruitment variation in a fish
stock. In poor recruitment years, the quota is set to zero and no fishing
is allowed. But any time there is a good recruitment pulse, a quota is
set that allows the fishery to exactly compensate through harvesting,
thereby maintaining the optimal escapement level. However, in that
analysis, Reed did not account for any costs of policy adjustment, which
for such a responsive management strategy potentially could be large.

@@

Empirics suggest not always as responsive as Reed solution. Explore
conditions under which that makes sense. Idea is that regulator's
objective sometimes may not be 'raw' NPV, but rather NPV with some
penalties on fast changes. Possible reasons: pure administrative
transaction cost of changing policies (reaching agreement), fishermens'
preferences for less variable quotas, processing plants' preferences for
less variable quotas especially if tied into contracts for canning and
so forth. But we do not know what functional form of any such policy
adjustment costs takes and it will be a lot of work to estimate it. Here
we explore several plausible candidate functional forms that each
reflect different ways these policy adjustment costs could work. Would
be good to know if differences between functional forms is particularly
important.

@@

We assume that managers choose annual quotas to maximize the expected
net present value (NPV) of the fishery. We take as a base case the
situation where there are no costs associated with policy adjustment and
the managers' objective is

@@

Taken together this objective function ([eq:objective]) and the state
equation ([eq:state_equation]) define a stochastic dynamic programming
problem that we solve using backwards recursion via Bellman's equation.
We denote the resulting state-dependent, optimal control as $h_0^{\ast}$.

@@

```{r Figure_1, fig.cap="Expected net present value by functional form of penalty. Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.  The horizontal line indicates a value of the stock that is 80% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.", dependson="quadcosts", fig.width=5, fig.height=3}
ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()

<!-- NOTE
Figure needs tidying up to be submission ready. Resize it - can be smaller, no color needed, bigger TickLabels, no background shading or grid. It also need the relevant horizontal and vertical lines marking to show the calibration. Choose a % reduction that corresponds to that you are choosing for what is currently labeled Figs 2&3 (sample paths) and Fig 8 - histograms. We should then adjust the text to talk to what is shown in the figure consistently - e.g. is is 25% loss or 75% of the value, etc. -->

@@

<!-- If, as discussed over email, we are going to go with just one in the main text blown up a bit bigger to make it more visible, I need to have that figure to be able to write this text around it. Note I would still present the full set in the SI. Rather than trying to recover old random seeds if not stored. Just run one anew. -->
<!-- 
For the figure in the main text, I would make a single figure with six plates - the three different adjustment costs are the columns. One row is the effect on optimal harvests and one the effect on optimal stock sizes. -->

@@

<!-- At what time relative to the dynamics in equation 1, and I would be setting up a comment why they don't see something similar to the constant escapement policy -- this is just a census time issue, but I would say it explicitly given the attention we shine on the REED result upfront.
-->

@@

When considering the first formulation of policy adjustment costs
($\Pi_1$), the first panel of Figure 2 shows a typical pattern, in which
the optimal policy tends to avoid small policy adjustments, resulting in
long periods of constant policy followed by sudden bursts of adjustment.
This results in a relatively step-like policy pattern. In contrast, the
second formulation $\Pi_2$ disproportionately penalizes large policy
adjustments. The corresponding optimal policy tracks all of the changes
made by the cost-free policy, but with smaller magnitude. This results
in a smoother $h_t$ curve, one that undershoots the larger oscillations
seen in the cost-free optimum in favor of a policy that changes
incrementally each year. Finally, the optimal policy for the third,
'fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one
might expect, because the magnitude of the adjustment made is not
reflected in the resulting penalty. Whereas the optimal solution for
$\Pi_1$ attempts to accommodate the large oscillations at the end of the
period shown (time steps $t=47-49$) with a constant quota in between the
extremes, the fixed fee version takes the opposite approach of one very
large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES

```{r Figure_2, dependson="tidy", fig.cap="Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics") +
  theme_bw()

```{r Figure_3, dependson="tidy", fig.cap="Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.", fig.height=3, fig.width=8}
ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics") + 
  theme_bw()

@@

<!--
Assuming we aren't showing cross-correlations, I think we can probably fit these into a single four subplot figure. Cross-correlations would be a little harder but just using 5 subplots from what could have been a 6 subplot figure would also work, because a journal could just put the caption into the empty space.

@@

```{r Figure_4, fig.cap="(a) Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. (b) Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + 
  xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4))

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4))

multiplot(Fig4a, Fig4b, cols=2)
```

```{r Figure_5, fig.cap = "(a) Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. (b) Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=3, fig.width=8}
Fig5a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4))

Fig5b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4))

multiplot(Fig5a, Fig5b, cols=2)

@@

-   Comparison between the different functional forms -- smoothing (L2)
    non-smoothing (L1), and de-stablizing (fixed).
